We are not the 99 percent: quantifying asphericity in the distribution of Local Group satellites

### 2018-02-07 paper/paper.tex
appendix figures

\begin{figure*}
\centering
\includegraphics[width=0.30\textwidth]{scatter_random_ranked_width.pdf}
\includegraphics[width=0.30\textwidth]{scatter_ranked_illudm_width.pdf}
\includegraphics[width=0.30\textwidth]{scatter_norm_ranked_illudm_width.pdf}
\caption{Plane width characterization in observations and
  simulations (Illustris1-Dark in this case.) In all panels the
  horizontal/vertical axis corresponds to the  M31/MW or the
  most/less massive halo in the pair 
  Left. Plane width in physical units comparing the results from observations
(stars) against the result of spherically randomizing the satellite
positions (circles). 
Middle. Average from the observations (star) and the average from each
pair in the simulation (circles).
Right. Same as the middle panel only that this time each point has
been normalized (median substracted and normalized by the standar
deviation) to the results of its randomization. 
The main message of these panels that the MW has a significantly
thiner plane both compared to the result of its own satellite
spherical randomization (left panel) and the expectation from
simulations (middle and right panel).  
This low value is $2\sigma$ away from what is expected in a spherical
distribution. 
In M31 the satellite distribution are in agreement with the
expectations both from an spherical distribution and the results form the
simulations. 
\label{fig:scatter_width}}
\end{figure*}
\begin{figure*}
\centering
\includegraphics[width=0.30\textwidth]{scatter_random_ranked_ca_ratio.pdf}
\includegraphics[width=0.30\textwidth]{scatter_ranked_illudm_ca_ratio.pdf}
\includegraphics[width=0.30\textwidth]{scatter_norm_ranked_illudm_ca_ratio.pdf}
\caption{Same layout as in Figure \ref{fig:scatter_width}. 
This time for the $c/a$ axis ratio. 
The same message holds in this case; namely, that 
the MW is has a significantly lowwe $c/a$ value than the
expectation from the spherical distribution and the simulations. 
This low value is also $2\sigma$ away from the expactations for an
spherical distribution.
On the other hand, M31 is consistent both with an spherical
distribution and the results from simulations.
\label{fig:scatter_ca_ratio}}
\end{figure*}

@@

\section{Results from ELVIS}
\begin{figure*}
\centering
\includegraphics[width=0.30\textwidth]{scatter_ranked_elvis_width.pdf}
\includegraphics[width=0.30\textwidth]{scatter_ranked_elvis_ca_ratio.pdf}
\includegraphics[width=0.30\textwidth]{scatter_ranked_elvis_ba_ratio.pdf}
\includegraphics[width=0.30\textwidth]{scatter_norm_ranked_elvis_width.pdf}
\includegraphics[width=0.30\textwidth]{scatter_norm_ranked_elvis_ca_ratio.pdf}
\includegraphics[width=0.30\textwidth]{scatter_norm_ranked_elvis_ba_ratio.pdf}
\caption{ELVIs results for the quantities presented for the Illustris-1
  simulation in Figures  \ref{fig:scatter_width},
  \ref{fig:scatter_ca_ratio}, \ref{fig:scatter_ba_ratio}.
Upper row corresponds to the raw values from observations and
simulated pairs, while the second row normalizes the same values to
the mean and standard deviation on its spherically randomized
counterparts. 
\label{fig:scatter_elvis}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.45\textwidth]{gaussian_model_elvis_M31.pdf}
\includegraphics[width=0.45\textwidth]{gaussian_model_elvis_MW.pdf}
\caption{
Same layout as Figure \ref{fig:correlations_illustris}, this time
computed from the ELVIS data.
\label{fig:correlations_elvis}}
\end{figure*}

>>>>

\begin{figure*}
\centering
\includegraphics[width=0.30\textwidth]{scatter_random_ranked_width.pdf}
\includegraphics[width=0.30\textwidth]{scatter_ranked_illudm_width.pdf}
\includegraphics[width=0.30\textwidth]{scatter_norm_ranked_illudm_width.pdf}
\caption{Plane width characterization in observations and
  simulations (Illustris1-Dark in this case.) In all panels the
  horizontal/vertical axis corresponds to the  M31/MW or the
  most/less massive halo in the pair 
  Left. Plane width in physical units comparing the results from observations
(stars) against the result of spherically randomizing the satellite
positions (circles). 
Middle. Average from the observations (star) and the average from each
pair in the simulation (circles).
Right. Same as the middle panel only that this time each point has
been normalized (median substracted and normalized by the standar
deviation) to the results of its randomization. 
The main message of these panels that the MW has a significantly
thiner plane both compared to the result of its own satellite
spherical randomization (left panel) and the expectation from
simulations (middle and right panel).  
This low value is $2\sigma$ away from what is expected in a spherical
distribution. 
In M31 the satellite distribution are in agreement with the
expectations both from an spherical distribution and the results form the
simulations. 
\label{fig:scatter_width}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.30\textwidth]{scatter_random_ranked_ca_ratio.pdf}
\includegraphics[width=0.30\textwidth]{scatter_ranked_illudm_ca_ratio.pdf}
\includegraphics[width=0.30\textwidth]{scatter_norm_ranked_illudm_ca_ratio.pdf}
\caption{Same layout as in Figure \ref{fig:scatter_width}. 
This time for the $c/a$ axis ratio. 
The same message holds in this case; namely, that 
the MW is has a significantly lowwe $c/a$ value than the
expectation from the spherical distribution and the simulations. 
This low value is also $2\sigma$ away from the expactations for an
spherical distribution.
On the other hand, M31 is consistent both with an spherical
distribution and the results from simulations.
\label{fig:scatter_ca_ratio}}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.30\textwidth]{scatter_random_ranked_width.pdf}
\includegraphics[width=0.30\textwidth]{scatter_ranked_illudm_width.pdf}
\includegraphics[width=0.30\textwidth]{scatter_norm_ranked_illudm_width.pdf}
\caption{
\label{fig:physical}}
\end{figure*}

\section{Results from ELVIS and Illustris1}
\begin{figure*}
\centering
\includegraphics[width=0.28\textwidth]{scatter_ranked_elvis_width.pdf}
\includegraphics[width=0.28\textwidth]{scatter_ranked_elvis_ca_ratio.pdf}
\includegraphics[width=0.28\textwidth]{scatter_ranked_elvis_ba_ratio.pdf}
\includegraphics[width=0.28\textwidth]{scatter_norm_ranked_elvis_width.pdf}
\includegraphics[width=0.28\textwidth]{scatter_norm_ranked_elvis_ca_ratio.pdf}
\includegraphics[width=0.28\textwidth]{scatter_norm_ranked_elvis_ba_ratio.pdf}
\caption{ELVIs results for the quantities presented for the Illustris1-Dark
  simulation in Figures  \ref{fig:scatter_width},
  \ref{fig:scatter_ca_ratio}, \ref{fig:scatter_ba_ratio}.
Upper row corresponds to the raw values from observations and
simulated pairs, while the second row normalizes the same values to
the mean and standard deviation on its spherically randomized
counterparts. 
\label{fig:scatter_elvis}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.45\textwidth]{gaussian_model_elvis_M31.pdf}
\includegraphics[width=0.45\textwidth]{gaussian_model_elvis_MW.pdf}
\caption{
Same layout as Figure \ref{fig:correlations_illustrisdm}, this time
computed from the ELVIS data.
\label{fig:correlations_elvis}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.28\textwidth]{scatter_ranked_width.pdf}
\includegraphics[width=0.28\textwidth]{scatter_ranked_ca_ratio.pdf}
\includegraphics[width=0.28\textwidth]{scatter_ranked_ba_ratio.pdf}
\includegraphics[width=0.28\textwidth]{scatter_norm_ranked_width.pdf}
\includegraphics[width=0.28\textwidth]{scatter_norm_ranked_ca_ratio.pdf}
\includegraphics[width=0.28\textwidth]{scatter_norm_ranked_ba_ratio.pdf}
\caption{Same layout as Figure \ref{fig:scatter_elvis}, this time
  computed from the Illustris1 data.
\label{fig:scatter_illustris}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.45\textwidth]{gaussian_model_illustris_M31.pdf}
\includegraphics[width=0.45\textwidth]{gaussian_model_illustris_MW.pdf}
\caption{
Same layout as Figure \ref{fig:correlations_illustrisdm}, this time
computed from the Illustris1 data.
\label{fig:correlations_illustris}}
\end{figure*}
